---
title: Model estimation
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


## Regression summary and plots for DV = price
### Antwerp
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_antwerp

```
The negative median indicates that the residuals are skewed to the left.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~8%).


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_average_price[[1]])

```

### Amsterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_amsterdam

```
The negative median indicates that the residuals are skewed to the left.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~9%).


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_average_price[[2]])

```


### Berlin
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_berlin

```
The negative median indicates that the residuals are skewed to the left.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. 24% of the variance in the DV is explained by the model.

```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_average_price[[3]])

```


### Brussels
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_brussels

```
The negative median indicates that the residuals are skewed to the left.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~12%).

```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_average_price[[4]])

```



### Rotterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_rotterdam

```

The negative median indicates that the residuals are skewed to the left.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~12%). 


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_average_price[[5]])

```



## Regression summary for DV = average nights
### Antwerp
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_antwerp

```
The positive median indicates that the residuals are skewed to the right.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~1%).


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_avg_nights[[1]])

```


### Amsterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_amsterdam

```
The positive median indicates that the residuals are skewed to the right.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~3%).


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_avg_nights[[2]])

```


### Berlin
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_berlin

```
The positive median indicates that the residuals are skewed to the right.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, an extremely low percentage of the variance in the data is explained by the model (<1%).


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_avg_nights[[3]])

```


### Brussels
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_brussels

```
The positive median indicates that the residuals are skewed to the right.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, an extremely low percentage of the variance in the data is explained by the model (~1%).


```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_avg_nights[[4]])

```


### Rotterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_rotterdam

```
The positive median indicates that the residuals are skewed to the right.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, an extremely low percentage of the variance in the data is explained by the model (<1%).

```{r echo=FALSE}
load("../../gen/analysis/output/model_results.RData")

plot(all_lm_avg_nights[[5]])

```