---
title: Model estimation
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


## Regression summary for DV = price
### Antwerp
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_antwerp

```



### Amsterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_amsterdam

```

### Berlin
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_berlin

```

### Brussels
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_brussels

```



### Rotterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_price_rotterdam

```

The negative median indicates that the residuals are skewed to the left.

The difference between the magnitude of the first quartile (1Q) and the third quartile (3Q) indicate a skew to the left, too.

However, since the sample is large, we proceed with the model despite the fact that the normality assumption is violated.

The p-value of the F-statistic is below 0.05, which indicates that the model is significant. However, a very low percentage of the variance in the data is explained by the model (only ~4%). 





## Regression summary for DV = average nights
### Antwerp
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_antwerp

```


### Amsterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_amsterdam

```

### Berlin
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_berlin

```

### Brussels
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_brussels

```



### Rotterdam
```{r echo=FALSE}
load("../../gen/analysis/temp/model_estimation1.RData")

regression_avgnights_rotterdam

```
